\demes: a pain-free specification for complex demography

### 2021-06-11 paper.tex
Add GADMA and rough pass at the software table.

% local definitions
\newcommand{\msprime}[0]{\texttt{msprime}}
\newcommand{\stdpopsim}[0]{\texttt{stdpopsim}}
\newcommand{\demes}[0]{\texttt{demes}}
\newcommand{\Demes}[0]{\texttt{Demes}}
\newcommand{\YAML}[0]{\texttt{YAML}}
\newcommand{\moments}[0]{\texttt{moments}}
\newcommand{\dadi}[0]{\texttt{$\partial$a$\partial$i}}
\newcommand{\fwdpy}[0]{\texttt{fwdpy11}}
\newcommand{\slim}[0]{\texttt{slim}}

\newcommand{\aprcomment}[1]{{\textcolor{blue}{APR: #1}}}

@@

\title{\demes: a pain-free specification for complex demography}
\author[*]{Graham Gower}
\author[*]{Aaron P. Ragsdale}
\author[ ]{...Others here...}
\author[**]{Kevin Thornton}
\author[**]{Jerome Kelleher}
\affil[*,**]{Denote equal contribution}
\maketitle

@@

>>>>

% local definitions
\newcommand{\msprime}[0]{\texttt{msprime}}
\newcommand{\stdpopsim}[0]{\texttt{stdpopsim}}
\newcommand{\demes}[0]{\texttt{demes}}
\newcommand{\Demes}[0]{\texttt{Demes}}
\newcommand{\YAML}[0]{\texttt{YAML}}
\newcommand{\moments}[0]{\texttt{moments}}
\newcommand{\dadi}[0]{\texttt{$\partial$a$\partial$i}}
\newcommand{\fwdpy}[0]{\texttt{fwdpy11}}
\newcommand{\slim}[0]{\texttt{SLiM}}
\newcommand{\gadma}[0]{\texttt{GADMA}}

\newcommand{\aprcomment}[1]{{\textcolor{blue}{APR: #1}}}
\newcommand{\jkcomment}[1]{{\textcolor{red}{JK: #1}}}

@@

\title{\demes: a pain-free specification for complex demography}
\author[*]{Graham Gower}
\author[*]{Aaron P. Ragsdale}
\author[ ]{...Others here...}
\author[**]{Jerome Kelleher}
\author[**]{Kevin Thornton}
\affil[*,**]{Denote equal contribution}
\maketitle

@@

\begin{table}
\begin{center}
\begin{tabular}{llr}
\msprime & \citep{kelleher2016efficient} & Coalescent simulator \\
\stdpopsim & \citep{adrion2020community} & Library of standardised simulations \\
\fwdpy & \citep{thornton2014c++} & Forward-time simulator \\
\moments & \citep{jouganous2017inferring,ragsdale2019models}
    & Demographic inference \\
\dadi & \citep{gutenkunst2009inferring}  & Demographic inference \\
\gadma & \citep{noskova2020gadma}  & Demographic inference \\
\end{tabular}
\end{center}
\caption{Software supporting Demes as an input or output format.
\jkcomment{This is a very rough first pass. It's not clear that a table is the
right format for presenting this information, maybe a description
list would be better instead?}}
\end{table}
